Classless Java

### 2016-03-21 OOPSLA16/sections/Implementation.tex
Fix figure 4.
Implementation

\section{A practical bridge between IB and CB}

\begin{figure}[t]\label{fig:lombok}
\centering
\includegraphics[width=3in]{pdfs/lombok.png}
\caption{The flow chart of Lombok annotation processing. [Ref: http://notatube.blogspot.hk/2010/12/project-lombok-creating-custom.html]
\marco{I'm not sure this helps: It is trying to show the "eclipse" path, that is the one we implemented,
but there is also the "javac" path, and here we call the graph "Lombok annotation processing".
May be this should be "obj" processing?
}}
\end{figure}

Even if convinced of the advantages of IB,
the practical convenience
of using existing libraries points us into building IB support
inside of an opportune CB language.\footnote{
Rewriting libraries and application in this language/model
would result in more reusable libraries, but it would be a taunting task.}

We believe Java is a good language for such integration, since it supports compilation agents[citeSomehting].

That is, Java libraries can interact with the Java compilation process,
acting as a man in the middle between the 
generation of the abstract syntax tree and the Java Bytecode.
\marco{is this correct?}
This process is facilitated by frameworks like Lombock~\cite{lombok}:
a Java library that aims at removing (or
reducing) Java boilerplate code via
annotations.
Figure~\ref{fig:lombok}\haoyuan{Wrong ref?} illustrates the
flow of \mixin annotation processing in Lombok.
%There are a number of annotations provided by the
%original Lombok, including \Q:@Getter:, \Q:@Setter:,
%\Q:@ToString: for generating getters, setters and \QM{toString}
%methods, respectively.  Furthermore, Lombok provides a number of
%interfaces for users to create custom transformations, as extensions
%to the original framework.
%A transformation is based on a handler, which acts on the AST for the
%annotated node and returns a modified AST for analysis and
%generation afterwards. Such a handler can either be a Javac handler or
%an Eclipse handler.

>>>>

\section{Bridging between IB and CB in Java}

\begin{figure}[t]\label{fig:lombok}
\centering
\includegraphics[width=3in]{pdfs/lombok.png}
\caption{The flow chart of Lombok annotation processing. [Ref: http://notatube.blogspot.hk/2010/12/project-lombok-creating-custom.html]
\marco{I'm not sure this helps: It is trying to show the "eclipse" path, that is the one we implemented,
but there is also the "javac" path, and here we call the graph "Lombok annotation processing".
May be this should be "obj" processing?
}}\bruno{The figure is blurred and the font size is too
small. Hoayuan, please improve the figure.}
\end{figure}

Even if convinced of the advantages of IB, the practical convenience
of using existing libraries points us into building IB support inside
of an opportune CB language like Java.
%\footnote{ Rewriting libraries and
%  application in this language/model would result in more reusable
%  libraries, but it would be a taunting task.}
While creating a new language or language extension would also
illustrate the point of IB (and would be more elegant), it would also
require significant amounts of engineering to achieve a similar level
of integration and tool support as Java.
This section illustrates how we integrate IB directly into Java instead. 
Disciplined use

\subsection{Compilation Agents}

Java is a good language for such integration, since it supports compilation agents\cite{compilationagents}.
That is, Java libraries can interact with the Java compilation process,
acting as a man in the middle between the 
generation of the abstract syntax tree and the Java Bytecode.
\marco{is this correct?}
This process is facilitated by frameworks like Lombock~\cite{lombok}:
a Java library that aims at removing (or
reducing) Java boilerplate code via
annotations.
Figure~\ref{fig:lombok}\haoyuan{Wrong ref?} illustrates the
flow of \mixin annotation processing in Lombok.
%There are a number of annotations provided by the
%original Lombok, including \Q:@Getter:, \Q:@Setter:,
%\Q:@ToString: for generating getters, setters and \QM{toString}
%methods, respectively.  Furthermore, Lombok provides a number of
%interfaces for users to create custom transformations, as extensions
%to the original framework.
%A transformation is based on a handler, which acts on the AST for the
%annotated node and returns a modified AST for analysis and
%generation afterwards. Such a handler can either be a Javac handler or
%an Eclipse handler.
